Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-08 aistats.tex
notation questions

\hypersetup{draft}

@@

\begin{theorem}[MAP Bound]
 For $n\in \naturalnumbers$, let us  define
 \begin{align}
	b_n = \frac{(1 + \inv{n_0} - \frac{\m_0}{\m^*})^2}{2 (\frac{\m_0}{\m^*}+\frac{(n-2)_+}{n_0})(1 + \frac{n}{n_0} )} \; .
 \end{align}
The expected suboptimality of the MAP of $\cN(0,\m^*)$ with prior hyper-parameters $(n_0,\m_0)$ is
 \begin{equation}
	\expect{\bregmanconj( \m_*; \hat \m_n^\text{MAP})}
	\leq \begin{cases}
		\inv{2(n_0+1)}  +  b_1 \ \text{if}\ n=1,\\
		\frac{1}{n_0 \frac{\m_0}{\m^*} +n-2} + b_n \ \text{if}\ n\geq 2
	\end{cases}
	\label{eq:MAP_rate}
\end{equation}
\end{theorem}

@@

>>>>

%\hypersetup{draft}

@@

\begin{theorem}[MAP Bound]
 For $n\in \naturalnumbers$, let us  define
 \begin{align}
	b_n = \frac{(1 + \inv{n_0} - \frac{\m_0}{\m^*})^2}{2 (\frac{\m_0}{\m^*}+\frac{(n-2)_+}{n_0})(1 + \frac{n}{n_0} )} \; .
 \end{align}
The expected suboptimality of the MAP of $\cN(0,\m^*)$ with prior hyper-parameters $(n_0,\m_0)$ is
 \begin{equation}
	\expect{\bregmanconj( \m_*; \hat \m_n^\mathrm{MAP})}
	\leq \begin{cases}
		\inv{2(n_0+1)}  +  b_1 \ \text{if}\ n=1,\\
		\frac{1}{n_0 \frac{\m_0}{\m^*} +n-2} + b_n \ \text{if}\ n\geq 2
	\end{cases}
	\label{eq:MAP_rate}
\end{equation}
\end{theorem}

@@

\newpage
\section{Notation convention}
We use 
\begin{itemize}
	\item $\theta, \nat$ for natural parameters
	\item $\m$ for mean parameters
	\item $X_1,\ldots,X_n$ for data
	\item $\cX$ for the data space 
	\item $T$ for the sufficient statistics
	\item $\nu$ for the base measure
	\item $A, A^*$ for the log-partition and its dual
	\item $\cB_A$ for the Bregman divergence induced by $A$
	\item $n$ for the number of samples
	\item $(\theta^*,m^*)$ for the optimum
	\item $\gamma$ for the step-size
	\item $\mu,\sigma^2$ for the parameters of a Gaussian
	\item $\hat\theta_n$ for estimates
	\item $\tilde\theta_n$ for $\expect{\hat\theta_n}$, which is biased
	\item $(L, \mu)$ for strong-convexity and smoothness 
\end{itemize}

\fdk{
	Do we use $\alpha, \beta$ anywhere? 
	Might use those for smoothness/strong-convexity rather than $\mu, L$.
} 
\fdk{
	The superscript ${}^*$ denotes the convex conjugate when applied on a function 
	and the optimum when applied to a parameter. 
	How about we use $\theta_n, \theta_*$ for parameter at time $n$ and at the optimum 
	and $f^*$ for the convex conjugate?
}
\fdk{
	On $X_i$ for data; I'm more used to seeing $x_i$ for data, which is the realization of the random variable $X_i$. 
	We don't talk about random variables and don't need the distinction? 
}
